---
title: "Choropleth map of presidential election results of 1980 "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
library(ggplot2)
library(tidyverse) 
library(kableExtra)
library(grid)
library(gridExtra)
library(dplyr)
library(spData)
library(ggmap)
library(maps)
library(mapview)
library(leaflet)
library(ggmap)
library(viridis)
```

##  Choropleth map
We are going to use the ``elect80`` data set which contains the Presidential election results of 1980 covering 3,107 US counties using geographical coordinates. 
First of all, we are going to use the FIPS codes to find the exact state and county. We are going to use the ``county.fips`` function which is a database matching FIPS codes to maps package county and state names.After matching our two dataframes we drop the columns and keep the region and pc_turnout variables.
To plot the outlines of a geographical region, we use ggplot2::map_data(). This will extract coordinate data from the maps library, to create a data frame containing the boundaries of one of a selection of geographical regions. Once we have the coordinates for the boundaries of our spatial regions, we can match this to the values of our spatial variable of interest using one of the ‘mutating joins’ from the dplyr library.

```{r, echo=FALSE,out.width = '70%',warning=FALSE}
##Choropleth map
states_data<-us_states_df %>% select(state,median_income_10)
states_data$state<-tolower(states_data$state)
##States
states_map <- map_data("state")
fact_join <- states_map %>% left_join(states_data, by=c('region'='state'))
#Visualise 
ggplot(fact_join, aes(long, lat, group = group))+
  geom_polygon(aes(fill = `median_income_10`), color = "white")+ theme_void()+
  scale_fill_viridis(breaks=c(36000,34000,32000,30000,28000,26000,24000,22000,20000),
                     guide = guide_legend(label.position = "right",title = 'Median Income', title.position = 'top', nrow=8))+
  labs(title = "State-level median income across the United States",subtitle = "Reported in 2010") +
    theme(text = element_text(color = "#22211d"),
          legend.background = element_rect(fill = "#f5f5f2", color = NA),
          plot.title = element_text(size= 14, hjust=0.01, color = "#4e4d47",
                                    margin = margin(b = -0.1, t = 0.4, l = 2, unit = "cm")))
```
