---
title: "Choropleth map of US states median income in 2010 "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
library(ggplot2)
library(tidyverse) 
library(kableExtra)
library(grid)
library(gridExtra)
library(dplyr)
library(spData)
library(ggmap)
library(maps)
library(mapview)
library(leaflet)
library(ggmap)
library(viridis)
```

We are going to use the ``us_states_df`` data set, that can be found in the spData package in R  which contains the state-level median income across the United States in 2010 from the American Community Survey (ACS).

First of all, we are going to use the FIPS codes to find the exact state and county. We are going to use the ``county.fips`` function which is a database matching FIPS codes to maps package county and state names.After matching our two dataframes we drop the columns and keep the region and pc_turnout variables.

To plot the outlines of a geographical region, we use ggplot2::map_data(). This will extract coordinate data from the maps library, to create a data frame containing the boundaries of one of a selection of geographical regions. Once we have the coordinates for the boundaries of our spatial regions, we can match this to the values of our spatial variable of interest using one of the ‘mutating joins’ from the dplyr library.

```{r, echo=TRUE,out.width = '70%',warning=FALSE}
##Choropleth map
states_data<-us_states_df %>% select(state, median_income_10)
states_data$state<-tolower(states_data$state)
##States
states_map <- map_data("state")
fact_join <- states_map %>% left_join(states_data, by=c('region'='state'))
#Visualise 
ggplot(fact_join, aes(long, lat, group = group))+
  geom_polygon(aes(fill = `median_income_10`), color = "white")+ theme_void()+
  scale_fill_viridis(breaks=c(36000,34000,32000,30000,28000,26000,24000,22000,20000),
                     guide = guide_legend(label.position = "right",title = 'Median Income', title.position = 'top', nrow=8))+
  labs(title = "State-level median income across the United States",subtitle = "Reported in 2010") +
    theme(text = element_text(color = "#22211d"),
          legend.background = element_rect(fill = "#f5f5f2", color = NA),
          plot.title = element_text(size= 14, hjust=0.01, color = "#4e4d47",
                                    margin = margin(b = -0.1, t = 0.4, l = 2, unit = "cm")))
```
